\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-09 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Petites corrections d’accents

First, we run a comparative statics analysis following a reduction in variable transport costs based on our estimates in 1974 and 2019, by transport mode. Specifically, we contrast two cases: In the first scenario \textit{\grave{a} la M\'{e}litz}, we assume that only ad-valorem costs apply. We hence apply the estimated reduction in total variable transport costs ``as if'' it was solely attributable to the ad-valorem component. In the second scenario \textit{\grave{a} la Hummels}, we rely of the true estimates of transport costs, with the reduction of total transport costs coming from both additive and ad-valorem components. The consequences of the reduction in international transport costs through both its additive and ad-valorem components. Importantly, we run this comparative statics analysis \textit{ceteris paribus}, notably with the same value of the export fixed cost $f_x$ as in the initial equilibrium (see Table \ref{tab:calib_horsTC}.

>>>>

First, we run a comparative statics analysis following a reduction in variable transport costs based on our estimates in 1974 and 2019, by transport mode. Specifically, we contrast two cases: In the first scenario \textit{à la Mélitz}, we assume that only ad-valorem costs apply. We hence apply the estimated reduction in total variable transport costs ``as if'' it was solely attributable to the ad-valorem component. In the second scenario \textit{à la Hummels}, we rely of the true estimates of transport costs, with the reduction of total transport costs coming from both additive and ad-valorem components. The consequences of the reduction in international transport costs through both its additive and ad-valorem components. Importantly, we run this comparative statics analysis \textit{ceteris paribus}, notably with the same value of the export fixed cost $f_x$ as in the initial equilibrium (see Table \ref{tab:calib_horsTC}.
